Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-14 paper/main.tex
Updated Table 1 - Serial Num ad Specs

\begin{table}[h!]
  \centering
  \caption{Hardware Inventory}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Hardware} & \textbf{Serial Number} & \textbf{Purpose} & \textbf{Specs} \\ \hline
  Arduino MKR WiFi & SN12345 & Connectivity & WiFi-enabled microcontroller board \\ \hline
  Arduino MKR GPS  & SN67890 & Location Tracking & Integrated GPS module \\ \hline
  DFRobot Solar Power Manager & SN11223 & Power Regulation & Manages and distributes solar cell and battery \\ \hline
  Solar Panel 70x100 mm & SN44556 & Energy Generation & 70x100 mm panel, 5W output \\ \hline
  Sparkfun Fuel Gage & SN77889 & Fuel Level Monitoring & Analog sensor for fuel measurement \\ \hline
  LiPo Battery & HXJNLDC & Energy Storage & 3.7V, 2100mAh capacity \\ \hline
  \end{tabular}
  \label{tab:hardware_inventory}
  \end{table}

>>>>

\begin{table}[h!]
  \centering
  \caption{Hardware Inventory}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Hardware} & \textbf{Serial Number} & \textbf{Purpose} & \textbf{Specs} \\ \hline
  Arduino MKR WiFi 1010 & ABX00023 & Connectivity & WiFi-enabled microcontroller board \\ \hline
  Arduino MKR GPS Shield & ASX00017 & Location Tracking & Integrated GPS module \\ \hline
  DFRobot Solar Power Manager & TPX00046 & Power Regulation & Manages and distributes solar cell and battery \\ \hline
  Solar Panel & TPX00181 & Energy Generation & 75x100x2.9 mm panel, 5W output \\ \hline
  Sparkfun Fuel Gage & 1568-1273-ND & Fuel Level Monitoring & Analog sensor for fuel measurement \\ \hline
  LiPo Battery & 2528 & Energy Storage & 3.7V, 2000mAh capacity \\ \hline
  \end{tabular}
  \label{tab:hardware_inventory}
  \end{table}
